Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2021-04-06 paper/ucl_tbr_paper.tex
nicer typesetting with the savetrees package
reduce keyword count

\usepackage{siunitx}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
\usepackage{isotope}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tabularx}

@@

\keywords{machine learning, surrogate model, regression, fast approximation,
Monte Carlo simulation, OpenMC, Paramak, tritium breeding, adaptive sampling}
\submitto{\NF}
\maketitle
\ioptwocol

>>>>

\usepackage{siunitx}
\usepackage{isotope}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage[all=normal,bibbreaks=tight,floats=tight,mathspacing=tight,wordspacing=tight]{savetrees}

@@

\keywords{Machine Learning, Surrogate Model, Tritium Breeding, Regression, Fast Approximation, Adaptive Sampling}
\submitto{\NF}
\maketitle
\ioptwocol
